

\documentclass[a4paper,12pt,twoside]{book}
\usepackage[english]{babel}
\usepackage[utf8]{inputenc}
 
\pagestyle{headings}
 
\begin{document}
\section{The Man Comes Around}
And I heard as it were, the noise of thunder.  One of the four beasts saying: come and see!
 
And I saw! 
 
And behold, a white horse.
 
\chapter{Chapter 1: The Hard Worker}
There was a man who was renowned for both his hard work and his passion for what he did.  

He grew up in Central America, his father working as a Civil Engineer; building dams, bridges, and following the work created by the industrialization of the South Americas.  From evading bus robbers in the rural parts of Columbia to learning a new language in a foreign country, to dropping water balloons on cars from the window of his family's apartment, his childhood was filled with happy memories which grew him into a man who loved pursuing challenges and solving problems.

His name was Ethan, and he graduated high school in Boston, then attended college on a scholarship from the Air Force, later dropping out of the Air Force Academy.

Graduating from Cal Tech with a degree in Electrical Engineering, he created a company which was similar to Yelp, but long before Yelp, or even the internet was considered part of life in the average household.  

The site allowed small restaurants to make themselves more discoverable on a public domain, which offered a revolutionary new market.  Unfortunately, the company was, in many ways, ahead of its time, and no restauraunt owners saw need or demand for a means of marketing themselves on a niche technology. 

After roughly two million dollars of investment into the start-up between six people, the company went under and was declared bankrupt.  Several months of toil, anxiety, meetings with investors, and personal savings were poured out, with nothing to show for.

However, lessons were learned, the six friends parted ways on good terms, and Ethan re-entered the workforce, working towards a Ph.D at University of Michigan, Ann Arbor, and taking a job as a lecturer at HKUst.

From the failed start-up, he learned how to allocate and assign resources more efficiently, decided to hire based solely on merit, and in his work, kept his eyes open for the next technology that the world was in need of.




\chapter{Chapter 2: A New Start}
Ethan knew he was a hardworking and creative man, but he also knew he was only one of many hardworking and creative men. He needed something more in order to fulfull his dreams of creating something great.

As an assistant lecturer for an information systems class, he interacted with students often, especially during office hours, and through these conversations he often heard tidbits of their busy and exciting lives. His student's lives were exciting - their ideas for random startups enriched his pool of ideas. While their lives were hectic, his plan for the future was busier, so he would utilize the students to do little tasks. 

In fact, his math hours became more of a startup company like enviornment - he began to assign students to tasks outside their homework to further his start up idea of the year - unique M&M flavored instant ramen cups. He was inspired by John, his lead student who came into every office hours except the one on Friday, who had an unhealthy obsession with M&Ms and other chocolate candies. Ethan was not a fan of chocolate, but was a fan of ramen, therefore combined the two ideas. 

M&Ms and ramen happened to be named the two most addicting items of the year, which was what the startup was based on. Ethan had a loose plan - at the upcoming university's dead week, he would distribute one thousand free cups to zombie like students and get them addicted on the M&M flavored ramen. The students would be so tired from studying for finals that anything, especially instant M&M flavored ramen, would become their comfort food. 

\chapter{Chapter 3: A Lost Treasure}

As Ethan continued giving orders to his visiting office hour students, John soon realized Ethan's ambition to create a start up company. John had a few choices - he could steal Ethan's idea and make his own startup, or jump on helping Ethan's startup become a booming success. However, he had no connections or resources, and understood that sticking with Ethan for the time being would be for the best. And so, John was Ethan's right hand man throughout the process. 

Soon, the university's dead week arrived, and the M&M flavored ramen was a success. The only draw back, as John and Ethan discovered, was the constant lingering smell of the weird ramen smell. John also had a girlfriend at the time, and while she was supporrtive of the start up, demanded that Ethan and John change the smell of the M&M ramen to roses, unless John wanted to break up. The girlfriend, as always, got her way. 

With that, the M&M ramen became rose-smelling M&M ramen, the top sensation of the year. It was a trend everywhere - in Los Angeles, Tokyo, and even Hamburg. Ethan and John became overnight super stars, invited to be the cover of magazines, talk with Oprah on her show, and became near millionaires. However, as a student and graduate of highly sought universities, John and Ethan used their financial analysis skills to predict that the rose-smelling M&M ramen trend would not last long. With that thought, they quickly sold the buisness to Obama, who had time to spare after retiring from presidency. Walking away set for life, John and Ethan began to wonder what would be the next chapter of their lives. 



\chapter{Chapter 4: Ecclesiastes}

The following June, four weeks after IPO and three days after the IPO party, the man sat at his home, and looked over his life.  32 years of hard work, love from his parents, frienship with his collegemates, and pursuit of his passion had paid off.  Looking ahead, he considered the accquiring of two small companies in the LA area, the soon and much-needed renovation of his house, and the upcoming family reunion in Northern California.  

In addition to the promising development of his company, his wise investments from several years' earlier in small, unheard-of companies like Uber and Bitcoin had paid off, with dividends.  

The man thought to himself, ‘What shall I do, for I have much more than I need to support my lifestyle?’ And he said, ‘I will do this: I will sell all my stocks and invest in new companies; I will buy some small properties and develop them to resell or rent out; this is how I will use and store up my goods.  And I will say to my soul, “Soul, you have ample goods laid up for many years; you live frugally, and you have a secure career doing what you love!.  Relax, eat, drink, be merry.”’ 


But God said to him, ‘Fool! This night your soul is required of you, and the things you have prepared, whose will they be?’ 

So is the one who lays up treasure for himself and does not consider the most important questions of life.
